### 2017-11-07 Draft2/Appendix.tex
Take care of Section 3
Work

\section{Proofs of $\TextTilde$ Properties}

\subsection{Merging over Arithmetic Operations}
\label{pf:MergesOverArithmetic}

\begin{proof}[Proof (Theorem \ref{thm:MergesOverArithmeticAdd})]
\end{proof}

\begin{proof}[Proof (Theorem \ref{thm:MergesOverArithmeticMultiply})]
	This can be easily shown by multiplying the limits corresponding to $\hat{f}$ and $\hat{g}$:

	\begin{align*}
	\lim_{n \to \infty} \frac{\hat{f}}{f} &= 1\\
	\lim_{n \to \infty} \frac{\hat{g}}{g} &= 1\\
	\left( \lim_{n \to \infty} \frac{\hat{f}}{f} \right) \left( \lim_{n \to \infty} \frac{\hat{g}}{g} \right) &= 1 \cdot 1\\
	\lim_{n \to \infty} \frac{\hat{f}\hat{g}}{fg} &= 1
	\end{align*}

	it follows that $\hat{f}\hat{g} \TextTilde fg$. The statement about division can be proved by flipping the fraction for $\hat{g}$ before multiplying, resulting in

	\begin{align*}
	\lim_{n \to \infty} \frac{\hat{f} / \hat{g}}{f / g} = 1
	\end{align*}

	This shows $\hat{f} / \hat{g} \TextTilde f / g$.
\end{proof}

@@

	it follows that $f + g \TextTilde f$.
\end{proof}

@@

\begin{proof}[Proof (Theorem \ref{thm:Transitivity})]
By definition, $\lim_{n \to \infty} g / f = 1$ and $\lim_{n \to \infty} h / g = 1$. Multiplying the two equations, $\lim_{n \to \infty} h / f = 1$ which implies $f \TextTilde h$.
\end{proof}

>>>>

\section{Proving $\sim$ Properties}

\subsection{$\sim$ Merges over $+$, $\times$, and $\div$}
\label{pf:MergesOverArithmetic}
\begin{proof}[Proof (Theorem \ref{thm:MergesOverOps})]
	The statement about multiplication can be shown easily by multiplying the limits corresponding to $f$ and $g$:
	\begin{align*}
	\lim_{n \to \infty} \frac{f}{\Tweak{f}} &= 1\\
	\lim_{n \to \infty} \frac{g}{\Tweak{g}} &= 1\\
	\left( \lim_{n \to \infty} \frac{f}{\Tweak{f}} \right) \left( \lim_{n \to \infty} \frac{g}{\Tweak{g}} \right) &= 1 \cdot 1\\
	\lim_{n \to \infty} \frac{fg}{\Tweak{f}\Tweak{g}} &= 1
	\end{align*}
	it follows that $fg \sim \Tweak{f}\Tweak{g}$. The statement about division can be proved by flipping the limit for $g$ before multiplying, resulting in
	\begin{align*}
	\lim_{n \to \infty} \frac{f / g}{\Tweak{f} / \Tweak{g}} = 1
	\end{align*}
	This shows $\dfrac f g \sim \dfrac {\Tweak{f}} {\Tweak{g}}$.
\end{proof}

@@

	it follows that $f + g \sim f$.
\end{proof}

@@

\begin{proof}[Proof (Theorem \ref{thm:Transitivity})]
By definition, $\lim_{n \to \infty} g / f = 1$ and $\lim_{n \to \infty} h / g = 1$. Multiplying the two equations, $\lim_{n \to \infty} h / f = 1$ which implies $f \sim h$.
\end{proof}

### 2017-11-07 Draft2/AsymptoticNotation.tex
Biconds
Work

I will mainly use the $\sim$ relation to analyze complexity. It is defined as follows:
\begin{align*}
f \sim g \leftrightarrow \lim_{n \to \infty} \frac f g = 1
\end{align*}
This is read as "$f$ is asymptotic to $g$" or "$f$ and $g$ are asymptotic." {\HdrNote} $f$ and $g$ are used as shorthand to denote $f(n)$ and $g(n)$, respectively.

@@

I will also introduce the cousins of $\sim$, $\FluteLess$ and $\FluteLeq$. $f \FluteLeq g$ if and only if $f \FluteLess g$ or $f \sim g$. $\FluteLess$ is defined as follows:
\begin{align*}
f \FluteLess g \leftrightarrow \lim_{n \to \infty} \frac f g < 1
\end{align*}
\subsection{Properties}
\label{subsec:AsymptoticProperties}

Here, I define various properties of the $\sim$ relation that will be used in my proofs. Proofs of these properties can be found in the appendix.

The following two theorems state that $\sim$ can "merge", or un-distribute, over arithmetic operations. This is a property shared with big-O.

\begin{theorem}
\label{thm:MergesOverArithmeticAdd}
	$P$ merges over addition and subtraction. That is, for functions $f$ and $g$,
	\begin{align*}
	(\hat{f} \sim f) \land (\hat{g} \sim g) \rightarrow \begin{cases}
		(\hat{f} + \hat{g}) \sim (f + g)\\
		(\hat{f} - \hat{g}) \sim (f - g)
	\end{cases}
	\end{align*}
\end{theorem}

\begin{theorem}
\label{thm:MergesOverArithmeticMultiply}
	$P$ merges over multiplication and division. That is, for functions $f$ and $g$,
	\begin{align*}
	(\hat{f} \sim f) \land (\hat{g} \sim g) \rightarrow \begin{cases}
	\hat{f}\hat{g} \sim fg\\
	\hat{f} / \hat{g} \sim f / g
	\end{cases}
	\end{align*}
\end{theorem}

The following theorem states that lower-order terms may be removed. For example, $(n + \log_2 n) \sim n$.

\begin{theorem}
\label{thm:RemovesLowerOrderTerms}
	If $\lim_{n \to \infty} g / f = 0$, then $f + O(g) \sim f$.
\end{theorem}

The following theorem shows that $\sim$ is a transitive relation. This property is used implicitly by proofs that chain multiple $\sim$s in the form $f \sim g \sim h$, then conclude that $f \sim h$.

>>>>

I will mainly use the $\sim$ relation to analyze complexity. It is defined as follows:
\begin{align*}
f \sim g \Biconditional \lim_{n \to \infty} \frac f g = 1
\end{align*}
This is read as "$f$ is asymptotic to $g$" or "$f$ and $g$ are asymptotic." {\HdrNote} $f$ and $g$ are used as shorthand to denote $f(n)$ and $g(n)$, respectively.

@@

I will also introduce the cousins of $\sim$, $\FluteLess$ and $\FluteLeq$. $f \FluteLeq g$ if and only if $f \FluteLess g$ or $f \sim g$. $\FluteLess$ is defined as follows:
\begin{align*}
f \FluteLess g \Biconditional \lim_{n \to \infty} \frac f g < 1
\end{align*}
\subsection{Properties}
\label{subsec:AsymptoticProperties}

Here, I define various properties of the $\sim$ relation that will be used in my proofs. These properties themselves are proved in the appendix.

The following theorem states that $\sim$ can "merge", or un-distribute, over addition, multiplication, and division. This is a property shared with big-O.

\begin{theorem}
\label{thm:MergesOverOps}
	Suppose $f$, $\Tweak{f}$, $g$, and $\Tweak{g}$ are functions. If $f \sim \Tweak{f}$ and $g \sim \Tweak{g}$, then
	\begin{align*}
	f + g &\sim \Tweak{f} + \Tweak{g}\\
	fg &\sim \Tweak{f}\Tweak{g}\\
	\frac{f}{g} &\sim \frac {\Tweak{f}} {\Tweak{g}}
	\end{align*}
\end{theorem}

The following theorem states that lower-order terms may be removed: for example, $(n + \log_2 n) \sim n$. This is also a property shared with big-O.

\begin{theorem}
\label{thm:RemovesLowerOrderTerms}
	If $\lim_{n \to \infty} \dfrac{g}{f} = 0$, then $f + O(g) \sim f$.
\end{theorem}

The following theorem states that $\sim$ is a transitive relation. This property is used implicitly by proofs that chain multiple $\sim$s in the form $f \sim g \sim h$, then conclude that $f \sim h$.
